Molecular Gas \old{Dynamics} \new{Kinematics and Spectral Energy Distribution Properties} of the Strongly-Lensed Quasar Host Galaxy RXS J1131$-$1231

### 2016-12-08 WRITEUP/diff.tex
ready for DR

% -------------------------------------- Final Edit Markup ----------------------------------
\usepackage[normalem]{ulem}
\usepackage{soul}
\usepackage[usenames]{xcolor}
\definecolor{OliveGreen}{cmyk}{0.64,0,0.95,0.40}
\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}
\newcommand{\new}[1]{\textcolor{blue}{\uwave{#1}}}
\newcommand{\old}[1]{\textcolor{red}{\st{#1}}} % {\textcolor{green!55!blue}{\bf #1}} or  {\textcolor{OliveGreen}{\bf #1}}
% -----------------------------------------------------------------------------------------------

@@

\title{Molecular Gas \old{Dynamics} \new{Kinematics} of the Strongly-lensed Quasar Host Galaxy RXS J1131$-$1231}
\author{T. K. Daisy Leung, Dominik A. Riechers, and Riccardo Pavesi}
\affil{Department of Astronomy, Space Sciences Building, Cornell University,
Ithaca, NY 14853, USA; \myemail}

@@

\defcitealias{Sluse03a}{S03}
The quasar RXS J113151.62$-$123158 (hereafter RXJ1131)
at $z_\textrm{s, QSO}$\eq$0.658$ \citep[hereafter S03]{Sluse03a} is a particularly well-suited source for
studying the evolution of molecular gas properties in quasar host galaxies and the
connection between SMBHs and their host galaxies at intermediate redshift
given its unique lensing configuration.
The stellar emission in the host galaxy of RXJ1131 is lensed into
an Einstein ring of $1$\farcs$83$ in radius
that is clearly separated from the quadruply imaged quasar emission \citep[hereafter C06]{Claeskens06a}.
The foreground lens is an elliptical galaxy at $z_\textrm{L}$\eq$0.295$ \citepalias{Sluse03a}.
 \citet[][]{Reis14a} report a high spin parameter of $a$\,$\sim$\,$0.9$ for the moderate-mass black hole in RXJ1131 \citep[$M_{\rm BH}$\eq$8$\E{7}\Msun;][]{Sluse12a}, %based on H beta line
with an intrinsic bolometric luminosity of $L_{\rm bol, X}$\eq$1.3$\E{45}\, ergs\,s\pmOne \citep{Pooley07a}.

In this paper, we present \bco and \cco line observations and
broadband photometry spanning rest-frame UV to radio wavelengths towards RXJ1131 to
study the properties of its molecular gas, dust and stellar populations.
In \Sec{obs}, we outline details of the observations and of our data reduction procedures.
In \Sec{results}, we report results for the \bco and \cco emission and broadband
photometry in RXJ1131.
In \Sec{anal}, we present lens modeling and dynamical modeling of the \bco data and
spectral energy distribution (SED) modeling of the photometric data.
In \Sec{diss}, we discuss
the ISM properties of the host galaxy of RXJ1131 and compare
them to other galaxy populations at low and high redshift.
Finally, we summarize the main results and present our conclusions in \Sec{sum}.
We use a concordance $\Lambda$CDM cosmology throughout this paper, with
parameters from the WMAP9 results:
$H_0$ = $69.32$ \kms Mpc\pmOne, $\Omega_{\rm M}$ = $0.29$, and
$\Omega_{\Lambda}$ = $0.71$ \citep{Hinshaw13a}.
% same as LR16a: i.e. use last column (WMAP+eCMB+BAO+H0) of Tab 4 in Hinshaw+13 because that's what astropy use for WMAP9 as cosmo
\defcitealias{Claeskens06a}{C06}

%--------------------------------------------------------------------------
%                          Observations details
%--------------------------------------------------------------------------
\section{Observations} \label{sec:obs}
\subsection{CARMA \cco}
Observations of the \cco rotational line \old{in RXJ1131} ($\nu_{\rm rest}$\,=\,345.79599\,GHz) redshifted to $\nu_{\rm obs}$\eq209.10443\,GHz \new{towards RXJ1131 at $z_{\rm QSO}$\eq0.658}
were carried out with the \carma (CARMA;
Program ID: cf0098; PI: D. Riechers)
in the D array configuration\new{. They were carried out} on 2014 February 02 under poor 1.5\,mm
weather conditions and on 2014 February 17 under good 1.5\,mm
weather conditions.
This resulted in a total on-source time of 2.94 hours after flagging poor
visibility data.
The correlator setup provides a bandwidth of 3.75 GHz in
each sideband and a %native
spectral resolution of 12.5 MHz ($\sim$17.9 \kms). The
line was placed in the lower sideband with the local oscillator tuned to $\nu_{\rm LO}\sim$216 GHz. The radio quasars J1127$-$189 (first track) and 3C273
(second track) were observed
every 15 minutes for pointing, amplitude, and phase calibration. Mars was
observed as the primary absolute flux calibrator and 3C279 was observed as
the bandpass calibrator for both tracks.

% poor phase note
% /Users/admin/Research/RXJ1131/CARMA/imagingD23/checkQuality.csh
% rms scatter over ~ 90 klambda
% max baseline of obs. is 145 m
%
% calflux source=1127-189 in=$MIRCAT/FluxSource.cat device=/xs
% Flux of: 1127-189  14FEB04.50 at 227.0 GHz:  0.65 Jy; rms: 0.10 Jy
% Extrapolate to 215.673 GHz with spectral index = -0.986 --> 0.684 Jy
% MIRIAD from bootstrap: Median Flux @ 215.673 GHz:     0.710 --> 3%
%
% amp de-correlation: % loss scales = 1- exp(-(50º*pi/180)^2 / 2) = ~32% loss
Given that the phase calibrator used for the first track was faint and was
observed under poor weather conditions and that the phase calibrator used for
the second track was far from our target source, the phase calibration is
subpar, with an rms scatter $\sim$50$\degr$ over a baseline length of $\sim$135\,m.
We thus conservatively estimate
a calibration accuracy of $\sim$40\% based on the flux scale uncertainties,    % ~40 = usual CARMA ~15-20% + 35% add in quad
the gain variations over time, and the phase scatter on the calibrated data. We
therefore treat the derived \cco line intensity with caution and ensure that our physical interpretation
of this system and the conclusion of this paper do not rely on this quantity.

The \ncode{miriad} package was used to calibrate the visibility data.
The calibrated visibility data were
imaged and deconvolved using the CLEAN algorithm with ``natural'' weighting. This yields a synthesized clean
beam size of 3\farcs2 $\times$ 1\farcs9 (PA\,=\,8\degr) for the lower sideband
image cube. The final rms noise is $\sigma$ = 13.3 mJy beam$^{-1}$
over a channel width of 25\,MHz. An rms noise of
$\sigma$\,=\,0.83\,mJy\,beam\pmOne is reached by averaging over the
line-free channels in both sidebands.

\subsection{PdBI \bco}
Observations of the \bco rotational line
($\nu_{\rm rest}$\,=\,$230.53800$ GHz)
\old{at the $\nu_{\rm LO}$\eq139.256\,GHz}
\new{redshifted to $\nu_{\rm obs}$\eq139.256\,GHz towards RXJ1131 at the CARMA \cco redshift of 
$z_{\rm CO(3-2)}$\eq0.655}
were carried out using IRAM \pdbi (PdBI; Program ID: S14BX; PI: D.
Riechers). Two observing runs were carried out on 2014 December 06 and 2015
February 05 under good weather conditions in the C and D array configurations,
respectively.
This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
 time after discarding unusable visibility data.
The 2 mm receivers were used to cover the redshifted \bco line
and the underlying continuum emission, employing a correlator setup that provides
an effective bandwidth of 3.6 GHz (dual polarization) and a native spectral resolution of 1.95\,MHz
($\sim$\,$4.2$\,\kms).
The nearby quasars B1127$-$145 and B1124$-$186 were observed every 22 minutes
for pointing, secondary amplitude, and phase calibration, and B1055$+$018 was
observed as the bandpass calibrator for both tracks.
MWC349 and 3C279 were observed as primary flux calibrators for the C and D
array observations, respectively, yielding calibration accuracy better than 15\%.

The \ncode{gildas} package was used to calibrate and analyze the visibility data.
The calibrated visibility data were imaged and deconvolved using the CLEAN algorithm with ``natural''
weighting. This yields a synthesized clean beam size of 4$\farcs$44 $\times$ 1\farcs95 (PA = 13\degr).
The final rms noise is $\sigma$\,=\,1.45\,mJy\,beam\pmOne
over 10 MHz (21.5\,\kms). The continuum image at $\nu_{\rm cont}\sim$139\,GHz
is produced by averaging over 3.16\,GHz of line-free bandwidth. This
yields an rms noise of 0.082 mJy\,beam$^{-1}$. % see README.md in 04Sep15

\subsection{VLA (Archival)}
Our analysis also uses archival data of the 4.885\,GHz %4.88510 GHz
radio continuum obtained with the
VLA (Program ID: AW741; PI: Wucknitz).
Observations were carried out on 2008 December 29 under excellent weather
conditions in the A array configuration for a total of $\sim$7 hours on-source time. The C-band receivers were used with a continuum mode setup,
providing a bandwidth of 50 MHz for the two IF bands with full polarization.
The nearby radio quasar J1130$-$149 was observed every 10 minutes for
pointing, amplitude, and phase calibration. J1331$+$305 was observed as the
primary flux calibrator, and J0319$+$415 was observed as the bandpass
calibrator, yielding $\sim$10\% calibration accuracy.
We used \ncode{aips} to calibrate the visibility data.
The calibrated visibility data were imaged and deconvolved using
the CLEAN algorithm with robust\,=\,0, which
was chosen to obtain a higher resolution image given high SNR.
This yields a synthesized clean
beam size of 0$\farcs$49 $\times$ 0\farcs35 (PA\,=\,0.18$\degr$) and a final
rms noise of $\sigma$ = 13 $\mu$Jy beam\pmOne.

@@

%--------------------------------------------------------------------------
%                                Results
%--------------------------------------------------------------------------
\section{Results} \label{sec:results}
\input{table_obsprop}

\subsection{\bco Emission} \label{sec:CO21}
We detect \bco line emission toward the background source in the PdBI data
at $\gtrsim$\,27$\sigma$ \old{significance, confirming} \new{significance. Based on this measurement, we refine} the redshift \old{at} \new{of RXJ1131 to} \old{$z_{\rm CO}$\eq0.6537\,$\pm$\,0.0005.}
\new{$z_{\rm CO}$\eq0.6541\,$\pm$\,0.0002\mbox{\footnote{This redshift is derived by fitting a double-Gaussian to
the de-lensed spectrum, which is shown in \Fig{delensed}
instead of the observed spectrum (\Fig{CO21spec}) to avoid biases in our 
redshift determination 
due to differential lensing (see \Sec{differential})}.}}
\old{The emission is spatially and dynamically resolved} \new{The emission is spatially and kinematically resolved}
with a highly asymmetric double-horned line profile
as shown in \Fig{CO21spec}. Fitting a double Gaussian results in peak
flux densities of 75.3\pmm2.6 mJy and 24.0\pmm2.0 mJy, and a FWHM of
179\pmm9 \kms and 255\pmm28 \kms for the two components, respectively. The peaks are separated by
$\Delta v_{\rm sep}$\eq400\pmm12\,\kms. The total integrated line flux is \old{24.1\,$\pm$\,2.3 Jy \kms} \new{20.3\,$\pm$\,0.6 Jy \kms}. % see 15May16/

\begin{figure}[htbp]
\centering
\includegraphics[width=0.45\textwidth]{../Figures/SpecCO21_twinx.eps}
\caption{Continuum-subtracted spectrum (histogram) of \bco emission towards RXJ1131, with a spectral resolution of
22\,\kms. The solid black line shows a double-Gaussian fit to the line profile.
The velocity scale is with respect to \old{$z$\,=\,0.6537, which is approximately the line center considering the asymmetry resulting from differential lensing.} \new{$z$\,=\,0.6541, which corresponds to the line center of RXJ1131 based on
the de-lensed line profile (\Fig{delensed})}.
A detailed discussion of this effect is presented in \Sec{differential}. \label{fig:CO21spec}}
\end{figure}
\vspace{.2em}
% moment 0 map, highest SNR: CASA chan=125~159 <=> GILDAS 126-160 <=> python 125-160
% - sigma = 0.305 Jy km/s/Beam
%   - note that theoretical sigma is lower = 1.5 * sqrt(160-126+1) * 21.5 ~ 0.2 Jy km/s /beam, due to higher noise in some channels with emission
We construct a zeroth order moment map, red/blue channel maps, and
first and second moment maps, as shown in \Fig{CO21mom},
using the $uv$-continuum subtracted data cube over a velocity range of
$\Delta v$ $\sim$ 750\,\kms.
The higher-order moment maps are produced using
unbinned channel maps with 3$\sigma$ clipping.
The peak flux density is 8.12\pmm0.30 Jy\,\kms\,beam\pmOne
in the intensity map.

\old{
The deconvolved source size FWHM obtained by fitting a two-dimensional Gaussian to the integrated line map in
the image plane
is 5\farcs1\pmm0\farcs72 $\times$ 3\farcs72\pmm0\farcs66,
and thus, the emission is resolved over $\sim$2.2 beams.
While the lensed emission is not strictly distributed as a two-dimensional
Gaussian;
the fit recovers the line intensity enclosed by the emitting
region, therefore we take this as an estimate on the full extent of the lensed
emission. On the other hand, if we assume that the spatial distribution of
the lensed molecular gas emission is similar to that in the optical to \mbox{\nir}
wavelengths, the lensed emission would be more accurately described by an
annulus, enclosing the partially complete ``Einstein ring'' and}
\old{\mbox{the lensed knots (see \Fig{CO21mom}).}}
\new{The deconvolved source size FWHM from fitting a single two-dimensional Gaussian 
to the integrated line image yields 5\farcs1\pmm0\farcs7$\times$3\farcs7\pmm0\farcs7,  % In the image plane, the *convolved* size is 6.6"+/-0.5" x 4.5"+/-0.3". 
consistent with that obtained by $uv$-plane fitting within the uncertainties. 
% UV plane: E_GAUSS: 4.5 +/- 0.1 x 3.5 +/- 0.2
The spatial distribution of the observed CO emission is unlikely to be fully 
encapsulated by a simple Gaussian 
given its skewed emission, which also appears to be a superposition of two components (\Fig{CO21mom}). 
% To better capture the spatial distribution of the line emission, we 
We therefore also fit a model of two Gaussians which yeilds deconvolved source sizes of 
3\farcs8\pmm0\farcs4$\times$1\farcs9\pmm0\farcs4 and 3\farcs6\pmm0\farcs3$\times$1\farcs5\pmm0\farcs3, respectively.
The deconvolved source size together with
% complex morphology of a partial ``Einstein ring'' with 
% structures along the arc and knots 
% seen in optical and \nir emission (see \Fig{CO21mom}). %that were observed at higher resolution, 
the spatially more extended blue wing compared to the optical 
``Einstein ring" of diameter $\sim$3\farcs6 (top right panel of \Fig{CO21mom}) suggest that 
the CO-emitting region in RXJ1131 is more extended than its stellar and quasar emission.}

\begin{figure*}[!htbp]
\hspace{0.5em}
% total chan range = 126-160, which is consistent with mom0 map now (see 15May16)
% 126-144 (Red)
% ~ delta V ~410 km/s
% from [409, 0] km/s
%  144-160 (Blue)
% ~ 365 km/s
% [-324.88, 0] km/s
\includegraphics[trim=0 10 15 0, clip, width=0.452\textwidth]{../Figures/F555WCO21_mom0_single_invertedgray.eps}
\includegraphics[trim=5 -18 0 0, clip, width=0.462\textwidth]{../Figures/F555W_REDBLUE.eps}
\\
\includegraphics[trim=25 16 0 10, clip, width=0.85\textwidth]{../Figures/CO_highOmom_CLIP5sigma}
\vspace{0.1em}
\caption{Top left: overlay of the velocity-integrated \bco emission on an archival {\it HST} $V$-band (F555W)
image.
Top right: same as top left, except the contours are color-coded to represent the red- and blueshifted emission, which
\old{\mbox{are extracted by integrating over $v$\,$\in$[0, 409] \kms and $\in$[$-$325,0] \kms, respectively.}}
\new{\mbox{are extracted by integrating over $v$\,$\in$[$-$19, 357] \kms and $\in$[$-$395, $-$19] \kms, respectively.}}
The contours in both top panels start at 3$\sigma$ and increment at steps of
$\pm$3$\sigma$, where $\sigma$\,=\,0.3 mJy beam\pmOne for the top left panel,
and
$\sigma$ = 0.4 mJy beam\pmOne (red) and 0.5 mJy beam\pmOne (blue)
for the top right panel.
The crosses denote the
location of the foreground galaxy at $z$\,=\,0.295.
Contours for the first (bottom left) and second (bottom right) moment maps of the \bco line emission
are shown in steps of
50 \kms, and 100 \kms, respectively.
The synthesis beam size is 4\farcs4 $\times$ 2\farcs0, at PA = 13$\degr$.
\label{fig:CO21mom}}
\end{figure*}

@@

\subsection{\cco Emission}
We detect \cco line emission towards RXJ1131 in the CARMA data at $\gtrsim$\,5$\sigma$ significance.
\old{The spectrum is shown in \mbox{\Fig{co32spec}} and appears to be consistent with a
double-peaked profile. }
\new{The \cco spectrum appears to be consistent with a double-peaked profile, as shown in \Fig{co32spec}, where we over-plot spectra of the \bco and \cco lines.}
\new{We extract the peak fluxes and their corresponding uncertainties for the blue and red wing independently.
We find a peak line flux of 5.13\pmm1.43 Jy\,\kms beam\pmOne for the blue wing, 
indicating a $\gtrsim$3$\sigma$ detection for this component, and a peak line 
flux of 11.45\pmm1.99\,Jy\,\kms beam\pmOne for the red wing, indicating a $\sim$\,6$\sigma$ detection. 
}
We estimate a line intensity of
\old{35.7\,$\pm$\,21.9 Jy\,\kms} \new{35.7\,$\pm$\,6.9\,Jy\,\kms (\Tab{obsprop})} by summing up fluxes over the FWZI
linewidth used to infer the \bco line intensity ($\sim$700 \kms).

>>>>

% -------------------------------------- Final Edit Markup ----------------------------------
\usepackage[normalem]{ulem}
\usepackage{soul}
\usepackage[usenames]{xcolor}
\definecolor{OliveGreen}{cmyk}{0.64,0,0.95,0.40}
\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}
\newcommand{\new}[1]{\textcolor{blue}{\uwave{#1}}}
\newcommand{\old}[1]{\textcolor{red}{\st{#1}}} % 
% -----------------------------------------------------------------------------------------------

@@

\title{Molecular Gas \old{Dynamics} \new{Kinematics and Spectral Energy Distribution Properties} of the Strongly-Lensed Quasar Host Galaxy RXS J1131$-$1231}
\author{T. K. Daisy Leung, Dominik A. Riechers, and Riccardo Pavesi}
\affil{Department of Astronomy, Space Sciences Building, Cornell University,
Ithaca, NY 14853, USA; \myemail}

@@

\defcitealias{Sluse03a}{S03}
The quasar RXS J113151.62$-$123158 (hereafter RXJ1131)
at $z_\textrm{s, QSO}$\eq$0.685$ \citep[hereafter S03]{Sluse03a} is a particularly well-suited source for
studying the evolution of molecular gas properties in quasar host galaxies and the
connection between SMBHs and their host galaxies at intermediate redshift
given its unique lensing configuration.
The stellar emission in the host galaxy of RXJ1131 is lensed into
an Einstein ring of $1$\farcs$83$ in radius
that is clearly separated from the quadruply imaged quasar emission \citep[hereafter C06]{Claeskens06a}.
The foreground lens is an elliptical galaxy at $z_\textrm{L}$\eq$0.295$ \citepalias{Sluse03a}.
\citet[][]{Reis14a} report a high spin parameter of $a$\,$\sim$\,$0.9$ for the moderate-mass black hole in RXJ1131 \citep[$M_{\rm BH}$\eq$8$\E{7}\Msun;][]{Sluse12a},
with an intrinsic bolometric luminosity of $L_{\rm bol, X}$\eq$1.3$\E{45}\, ergs\,s\pmOne \citep{Pooley07a}.

In this paper, we present \bco and \cco line observations and
broadband photometry spanning rest-frame UV to radio wavelengths towards RXJ1131 to
study the properties of its molecular gas, dust and stellar populations.
In \Sec{obs}, we outline details of the observations and of our data reduction procedures.
In \Sec{results}, we report results for the \bco and \cco emission and broadband
photometry in RXJ1131.
In \Sec{anal}, we present lens modeling and dynamical modeling of the \bco data and
spectral energy distribution (SED) modeling of the photometric data.
In \Sec{diss}, we discuss
the ISM properties of the host galaxy of RXJ1131 and compare
them to other galaxy populations at low and high redshift.
Finally, we summarize the main results and present our conclusions in \Sec{sum}.
We use a concordance $\Lambda$CDM cosmology throughout this paper, with
parameters from the WMAP9 results:
$H_0$ = $69.32$ \kms Mpc\pmOne, $\Omega_{\rm M}$ = $0.29$, and
$\Omega_{\Lambda}$ = $0.71$ \citep{Hinshaw13a}.
\defcitealias{Claeskens06a}{C06}

\section{Observations} \label{sec:obs}
\subsection{CARMA \cco}
\old{Observations of the \mbox{\cco} rotational line in RXJ1131
($\nu_{\rm rest}$\,=\,345.79599\,GHz) redshifted to $\nu_{\rm obs}$\eq209.10443\,GHz
were carried out with the \mbox{\carma} (CARMA;
Program ID: cf0098; PI: D. Riechers)
in the D array configuration on 2014 February 02 under poor 1.5\,mm
weather conditions and on 2014 February 17 under good 1.5\,mm
weather conditions.}
\new{Observations of the \cco rotational line 
($\nu_{\rm rest}$\,=\,345.79599\,GHz) towards RXJ1131 at $z_{\rm s, QSO}$\eq0.658 
were carried out with the \mbox{\carma} (CARMA;
Program ID: cf0098; PI: D. Riechers) in the D array configuration. 
The line frequency is redshifted to $\nu_{\rm obs}$\eq209.10443\,GHz at the quasar redshift.
Observations were carried out
on 2014 February 02 under poor 1.5\,mm
weather conditions and on 2014 February 17 under good 1.5\,mm
weather conditions.}
This resulted in a total on-source time of 2.94 hours after flagging poor
visibility data.
The correlator setup provides a bandwidth of 3.75 GHz in
each sideband and a
spectral resolution of 12.5 MHz ($\sim$17.9 \kms). The
line was placed in the lower sideband with the local oscillator tuned to $\nu_{\rm LO}\sim$216 GHz. The radio quasars J1127$-$189 (first track) and 3C273
(second track) were observed
every 15 minutes for pointing, amplitude, and phase calibration. Mars was
observed as the primary absolute flux calibrator and 3C279 was observed as
the bandpass calibrator for both tracks.

Given that the phase calibrator used for the first track was faint and was
observed under poor weather conditions and that the phase calibrator used for
the second track was far from our target source, the phase calibration is
subpar, with an rms scatter $\sim$50$\degr$ over a baseline length of $\sim$135\,m.
We thus conservatively estimate
a calibration accuracy of $\sim$40\% based on the flux scale uncertainties,    % ~40 = usual CARMA ~15-20% + 35
the gain variations over time, and the phase scatter on the calibrated data. We
therefore treat the derived \cco line intensity with caution and ensure that our physical interpretation
of this system and the conclusion of this paper do not rely on this quantity.

The \ncode{miriad} package was used to calibrate the visibility data.
The calibrated visibility data were
imaged and deconvolved using the CLEAN algorithm with ``natural'' weighting. This yields a synthesized clean
beam size of 3\farcs2 $\times$ 1\farcs9 \old{(PA\,=\,8\degr)} \new{at a position angle (PA) of 8\degr} for the lower sideband
image cube. The final rms noise is $\sigma$ = 13.3 mJy beam$^{-1}$
over a channel width of 25\,MHz. An rms noise of
$\sigma$\,=\,0.83\,mJy\,beam\pmOne is reached by averaging over the
line-free channels in both sidebands.

\subsection{PdBI \bco}
\old{Observations of the \mbox{\bco} rotational line
($\nu_{\rm rest}$\,=\,$230.53800$ GHz)
at the $\nu_{\rm LO}$\eq139.256\,GHz
were carried out using IRAM \mbox{\pdbi} (PdBI; Program ID: S14BX; PI: D.
Riechers). Two observing runs were carried out on 2014 December 06 and 2015
February 05 under good weather conditions in the C and D array configurations,
respectively.}
\new{Observations of the \bco rotational line
($\nu_{\rm rest}$\,=\,$230.53800$ GHz) 
towards RXJ1131
were carried out using IRAM \mbox{\pdbi} (PdBI; Program ID: S14BX; PI: D.
Riechers).
Based on the CARMA \cco line redshift of $z_{\rm CO(3-2)}$\eq0.655,
the \bco line is redshifted to $\nu_{\rm obs}$\eq139.256\,GHz.
}
This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
time after discarding unusable visibility data.
The 2 mm receivers were used to cover the redshifted \bco line
and the underlying continuum emission, employing a correlator setup that provides
an effective bandwidth of 3.6 GHz (dual polarization) and a native spectral resolution of 1.95\,MHz
($\sim$\,$4.2$\,\kms).
The nearby quasars B1127$-$145 and B1124$-$186 were observed every 22 minutes
for pointing, secondary amplitude, and phase calibration, and B1055$+$018 was
observed as the bandpass calibrator for both tracks.
MWC349 and 3C279 were observed as primary flux calibrators for the C and D
array observations, respectively, yielding calibration accuracy better than 15\%.

The \ncode{gildas} package was used to calibrate and analyze the visibility data.
The calibrated visibility data were imaged and deconvolved using the CLEAN algorithm with ``natural''
weighting. This yields a synthesized clean beam size of 4$\farcs$44 $\times$ 1\farcs95 (PA = 13\degr).
The final rms noise is $\sigma$\,=\,1.45\,mJy\,beam\pmOne
over 10 MHz (21.5\,\kms). The continuum image at $\nu_{\rm cont}\sim$139\,GHz
is produced by averaging over 3.16\,GHz of line-free bandwidth. This
yields an rms noise of 0.082 mJy\,beam$^{-1}$.

\subsection{VLA (Archival)}
Our analysis also uses archival data of the 4.885\,GHz
radio continuum obtained with the
VLA (Program ID: AW741; PI: Wucknitz).
Observations were carried out on 2008 December 29 under excellent weather
conditions in the A array configuration for a total of $\sim$7 hours on-source time. The C-band receivers were used with a continuum mode setup,
providing a bandwidth of 50 MHz for the two IF bands with full polarization.
The nearby radio quasar J1130$-$149 was observed every 10 minutes for
pointing, amplitude, and phase calibration. J1331$+$305 was observed as the
primary flux calibrator, and J0319$+$415 was observed as the bandpass
calibrator, yielding $\sim$10\% calibration accuracy.
We used \ncode{aips} to calibrate the visibility data.
The calibrated visibility data were imaged and deconvolved using
the CLEAN algorithm with robust\,=\,0, which
was chosen to obtain a higher resolution image given high SNR.
This yields a synthesized clean
beam size of 0$\farcs$49 $\times$ 0\farcs35 (PA\,=\,0.18$\degr$) and a final
rms noise of $\sigma$ = 13 $\mu$Jy beam\pmOne.

@@

\section{Results} \label{sec:results}
\input{table_obsprop}

\subsection{\bco Emission} \label{sec:CO21}
We detect \bco line emission towards the background source RXJ1131 in the PdBI data
at $\gtrsim$\,27$\sigma$ significance\old{, confirming the redshift at $z_{\rm CO}$ =
0.6537\,$\pm$\,0.0005.} 
\new{. Based on this measurement, we refine the redshift of RXJ1131 to
$z_{\rm CO}$\eq0.6541\,$\pm$\,0.0002\mbox{\footnote{This redshift is derived by fitting a double-Gaussian to 
the de-lensed spectrum (\Fig{delensed}) 
instead of the observed spectrum (\Fig{CO21spec}) to avoid biases in our 
redshift determination 
due to differential lensing (see \Sec{differential}).
}.}}
The emission is spatially and \old{dynamically}\new{kinematically} resolved
with a highly asymmetric double-horned line profile
as shown in \Fig{CO21spec}. Fitting a double Gaussian results in peak
flux densities of 75.3\pmm2.6 mJy and 24.0\pmm2.0 mJy, and a FWHM of
179\pmm9 \kms and 255\pmm28 \kms for the two components, respectively. The peaks are separated by
$\Delta v_{\rm sep}$ = 400\pmm12\,\kms. The total integrated line flux is \old{24.1\,$\pm$\,2.3 Jy \kms}\new{20.3\,$\pm$\,0.6 Jy \kms}.

\begin{figure}[htbp]
\centering
\includegraphics[width=0.45\textwidth]{../Figures/SpecCO21_twinx.eps}
\caption{Continuum-subtracted spectrum (histogram) of \bco emission towards RXJ1131, with a spectral resolution of
22\,\kms. The solid black line shows a double-Gaussian fit to the line profile.
\old{The velocity scale is with respect to $z$\,=\,0.6537, which is approximately the line center
considering the asymmetry resulting from differential lensing.}
\new{The velocity scale is with respect to $z$\,=\,0.6541, which corresponds to the line center of RXJ1131 based on
the de-lensed line profile (\Fig{delensed}).}
A detailed discussion of this effect is presented in \Sec{differential}. \label{fig:CO21spec}}
\end{figure}
\vspace{.2em}
We construct a zeroth order moment map, red/blue channel maps, and
first and second moment maps, as shown in \Fig{CO21mom},
using the $uv$-continuum subtracted data cube over a velocity range of
$\Delta v$ $\sim$ 750\,\kms.
The higher-order moment maps are produced using
unbinned channel maps with 3$\sigma$ clipping.
The peak flux density is 8.12\pmm0.30 Jy\,\kms\,beam\pmOne
in the intensity map. \new{Observed properties of the \bco emission line are summarized in \Tab{obsprop}.}

\old{The deconvolved source size FWHM obtained by fitting a two-dimensional Gaussian to the integrated line map in
the image plane
is 5\farcs1\pmm0\farcs72 $\times$ 3\farcs72\pmm0\farcs66,
and thus, the emission is resolved over $\sim$2.2 beams.
While the lensed emission is not strictly distributed as a two-dimensional
Gaussian;
the fit recovers the line intensity enclosed by the emitting
region, therefore we take this as an estimate on the full extent of the lensed
emission. On the other hand, if we assume that the spatial distribution of
the lensed molecular gas emission is similar to that in the optical to \mbox{\nir}
wavelengths, the lensed emission would be more accurately described by an
annulus, enclosing the partially complete ``Einstein ring'' and
the lensed knots \mbox{(see \Fig{CO21mom}).}}
\new{The deconvolved source size FWHM obtained from fitting a single two-dimensional Gaussian 
to the integrated line emission in the image plane yields 5\farcs1\pmm0\farcs7$\times$3\farcs7\pmm0\farcs7,  
which is consistent with that obtained by visibility-plane fitting within the uncertainties. 
Since the spatial distribution of the observed CO emission is unlikely to be fully described by a simple Gaussian
and appears to be a superposition of two components (top left panel of \Fig{CO21mom}), 
we also fit two Gaussians to the intensity map. 
This yields deconvolved source sizes of 
3\farcs8\pmm0\farcs4$\times$1\farcs9\pmm0\farcs4 and 3\farcs6\pmm0\farcs3$\times$1\farcs5\pmm0\farcs3, respectively.
The deconvolved source sizes of both models suggest that the gravitationally lensed CO emission is more extended 
than the optical 
``Einstein ring'', which has a diameter of $\sim$3\farcs6
(i.e., the ``Einstein ring'' formed by CO emission is likely to have a larger diameter compared to the optical one). 
This is consistent with the centroid position of the redshifted emission, which is along the quasar arc seen in the optical image, 
and the blueshifted emission, which is offset further to the SE (top right of \Fig{CO21mom}).
Therefore, the CO-emitting region in RXJ1131 is likely to be more extended than its stellar and quasar emission.}

\begin{figure*}[!htbp]
\hspace{0.5em}
\includegraphics[trim=0 10 15 0, clip, width=0.452\textwidth]{../Figures/F555WCO21_mom0_single_invertedgray.eps}
\includegraphics[trim=5 -18 0 0, clip, width=0.462\textwidth]{../Figures/F555W_REDBLUE.eps}
\\
\includegraphics[trim=25 16 0 10, clip, width=0.85\textwidth]{../Figures/CO_highOmom_CLIP5sigma}
\vspace{0.1em}
\caption{Top left: overlay of the velocity-integrated \bco emission on an archival {\it HST} $V$-band (F555W)
image.
Top right: same as top left, except the contours are color-coded to represent the red- and blueshifted emission, which
\old{\mbox{are extracted by integrating over $v$\,$\in$[0, 409] \kms and $\in$[$-$325,0] \kms, respectively.}}
\new{\mbox{are extracted by integrating over $v$\,$\in$[$-$19, 357] \kms and $\in$[$-$395, $-$19] \kms, respectively.}}
The contours in both top panels start at 3$\sigma$ and increment in steps of
$\pm$3$\sigma$, where $\sigma$\,=\,0.3 mJy beam\pmOne for the top left panel,
and
$\sigma$ = 0.4 mJy beam\pmOne (red) and 0.5 mJy beam\pmOne (blue)
for the top right panel.
The crosses denote the
location of the foreground galaxy at $z$\,=\,0.295.
Contours for the first (bottom left) and second (bottom right) moment maps of the \bco line emission
are shown in steps of
50 \kms, and 100 \kms, respectively.
The synthesis beam size is 4\farcs4 $\times$ 2\farcs0, at PA = 13$\degr$.
\label{fig:CO21mom}}
\end{figure*}

@@

\subsection{\cco Emission}
We detect \cco line emission towards RXJ1131 in the CARMA data at $\gtrsim5\sigma$ significance.
\old{The spectrum is shown in \mbox{\Fig{co32spec}} and appears to be consistent with a
double-peaked profile. }
\new{The \cco spectrum appears to be consistent with a double-peaked profile, as shown in \mbox{\Fig{co32spec}}, where
we over-plot spectra of the \bco and \cco lines.
We extract the peak fluxes and their corresponding uncertainties for the blue and red wing independently.
We find a peak line flux of 5.13\pmm1.43 Jy\,\kms beam\pmOne for the blue wing, indicating a $\gtrsim$3$\sigma$ detection for this component alone, and a peak line flux of 11.45\pmm1.99\,Jy\,\kms beam\pmOne for the red wing, 
indicating a $\sim$\,6$\sigma$ detection. }
We estimate a line intensity of 
\old{35.7\,$\pm$\,21.9 Jy\,\kms} \new{35.7\,$\pm$\,6.9\,Jy\,\kms (\mbox{\Tab{obsprop}})}
by summing up fluxes over the FWZI
linewidth used to infer the \bco line intensity.

Assuming that the spatial extent of \bco and \cco is similar and therefore the emission is
magnified by the same amount, the measured line intensities
correspond to a brightness temperature ratio of
$r_{\rm 32}$\,=\,$T_{\small \cco}$$/$$T_{\small \bco}$\,=\,\old{0.66\,$\pm$\,0.41. Taking into account the large phase errors associated with \cco, this is consistent with}
\new{0.78\,$\pm$\,0.37. The quoted error bar is derived by adding the uncertainties associated with the CO line intensities 
and those from absolute flux calibrations in quadrature.
This brightness temperature ratio is consistent with} 
thermalized excitation within the uncertainties, as commonly observed in nuclear regions of
nearby ULIRGs and high-$z$ quasars \citep[e.g.,][]{Weiss07a, Riechers11b, CW13}, but also
with the lower excitation seen in normal star-forming disks \citep[e.g.,][]{Dannerbauer09a, CW13, Daddi15a}.
